Calibrating the pixel-level Kepler imaging data with a causal data-driven model \\

### 2015-02-23 cpm.tex
checked

@@

\title{%
  Self-calibration of time-domain imaging for exoplanet science, informed by causal structure%
  \\ or \\
  A data-driven, pixel-level model to improve the precision of \Kepler\ photometry%
  \\ or \\
  Exploiting causal structure to create a data-driven self-calibration of \Kepler\ imaging%
}
\author{%
  Dun~Wang\altaffilmark{\ref{CCPP}},
  Dan~Foreman-Mackey\altaffilmark{\ref{CCPP}},
  David~W.~Hogg\altaffilmark{\ref{CCPP},\ref{CDS},\ref{MPIA},\ref{email}},
  Bernhard~Sch\"olkopf\altaffilmark{\ref{MPIIS}},
  others%
}
\newcounter{address}
\setcounter{address}{1}
\altaffiltext{\theaddress}{\stepcounter{address}\label{CCPP}%
  Center for Cosmology and Particle Physics, Department of Physics, New York University}
\altaffiltext{\theaddress}{\stepcounter{address}\label{CDS}%
  Center for Data Science, New York University}
\altaffiltext{\theaddress}{\stepcounter{address}\label{MPIA}%
  Max-Planck-Institut f\"ur Astronomie, Heidelberg, Germany}
\altaffiltext{\theaddress}{\stepcounter{address}\label{email}%
  To whom correspondence should be addressed; \texttt{<david.hogg@nyu.edu>}.}
%% \altaffiltext{\theaddress}{\stepcounter{address}\label{Ames}%
%%   NASA Ames Research Center}
%% \altaffiltext{\theaddress}{\stepcounter{address}\label{Courant}%
%%   Courant Institute of Mathematical Sciences, New York University}
\altaffiltext{\theaddress}{\stepcounter{address}\label{MPIIS}%
  Max-Planck-Institut f\"ur Intelligente Systeme, T\"ubingen}
%% \altaffiltext{\theaddress}{\stepcounter{address}\label{Oxford}%
%%   Department of Physics, Oxford University}
%% \altaffiltext{\theaddress}{\stepcounter{address}\label{CfA}%
%%   Harvard--Smithsonian Center for Astrophysics}
%% \altaffiltext{\theaddress}{\stepcounter{address}\label{UCL}%
%%   Department of Physics and Astronomy, University College London}
%% \altaffiltext{\theaddress}{\stepcounter{address}\label{CMU}%
%%   McWilliams Center for Cosmology, Carnegie Mellon University}
%% \altaffiltext{\theaddress}{\stepcounter{address}\label{Caltech}%
%%   Department of Astronomy, California Institute of Technology}
%% \altaffiltext{\theaddress}{\stepcounter{address}\label{Columbia}%
%%   Department of Astronomy, Columbia University}

\begin{abstract}
The precision of \Kepler\ photometry for exoplanet science---the most
precise photometric measurements of stars ever made---appears to be
limited by unknown or untracked variations in spacecraft pointing and
temperature, and unmodeled stellar variability.
Here we present \name,
  a data-driven model of these variations in \Kepler\ data (or really of their impact on the photometry).
Importantly (and uniquely),
  \name\ works at the pixel level (not the photometric measurement level);
  it can capture more fine-grained information about the variation of the spacecraft
  (especially regarding pointing and point-spread function)
  than is available in the pixel-summed photometry.
\name\ is extreme in that it has enormous flexibility and it only uses data (and meta-data) to predict data:
\name\ provides a prediction for each readout pixel built from a linear combination of the readouts
  from very large numbers of nearby pixels (plus some spacecraft information);
  the choice of nearby pixels is guided by ideas from causal inference.
\name\ avoids over-fitting by employing a train-and-test formalism
  designed to ensure that transit-like photometric events and short-timescale stellar variability
  cannot be captured or distorted by the model;
  it is designed to remove spacecraft-induced variability but not intrinsic stellar variability.
We show that \name\ outperforms the \Kepler\ Presearch (\sic) Data Conditioning method on a set of example stars.
We release open-source code that provides \name\ output for any star in the existing \Kepler\ Archive,
  and we discuss applications for other missions,
  including any possible \Kepler\ two-wheel mission.
\end{abstract}

@@

One such method---one that is designed to describe or model spacecraft-induced problems
  but \emph{not} interfere with measurements of stellar variability---%
  is the \Kepler\ Presearch (\sic) Data Conditioning (PDC) method (\todo{citation}).
The PDC ``de-trends'' the \Kepler\ lightcurves by fitting them with a small set of basis lightcurves
  generated from a principal components analysis (PCA) of filtered lightcurves.
That is, it uses data to predict data,
  regularizing the fit (and avoiding over-fitting) by filtering and restricting the dimensionality (through PCA).
The method proposed here, \name, is very similar in spirit to the PDC.
The main differences are
  (1)~that \name\ works in the pixel domain, not the lightcurve domain, so it has access to more fine-grained information,
  (2)~that \name\ has far more freedom (far more parameters) than the PDC
  but it strictly avoids over-fitting the lightcurves on exoplanet-transit time-scales
  through strong regularization and a train-and-test framework, and
  (3)~that when \name\ fits a star, there is no possibility of any contribution of the star itself to the fit basis vectors.
The two methods (\name\ and PDC) are similar however,
  in that they both make the assumption that whatever spacecraft effects are imprinting variability on a stellar lightcurve
  must also be imprinting similar or related variability on other lightcurves.
They also assume that the relationships can be captured with linear models.
By going to the pixel level (unlike the PDC, which works at the photometry level),
  \name\ makes it easier for the model to capture variability
  that is coming through variations in the centroids and point-spread function
  from spacecraft pointing, roll, and temperature.

@@

\section{Data-driven models}

@@

The second general idea about data-driven modeling is the investigator's beliefs
  about the causal processes that generate the data
  are crucial in restricting the kinds of data that can be used as input to the model.
That is, different assumptions about the physical properties of the data
  and the data-taking system
  lead to different structures for the data-driven model.
For example, in the case of \Kepler\ data,
  if we believe that different stars in the \Kepler\ field vary independently
  (that is, are not physically synchronized in any way),
  then the only reason that one star might show variability that is strongly \emph{predictive}
  (useful for prediction) of another star's variability
  is that both stars are being observed by the same device or spacecraft.
That is, one star's pixels can be used to predict another star's pixels
  inasmuch as spacecraft issues imprint on both stars in related ways;
  they share a common cause.
For another example, if we think the spacecraft is being affected by
  processes that take place over time-scales longer than a single read-out
  (for example, thermal processes),
  then it would be sensible to model the data at time $t$ using not just simultaneous data,
  but also data from a range of times around $t$.
For another example, if an investigator doesn't care about preserving stellar variability,
  and just wants to detect exoplanet transits (say),
  pixels from the target star can be used to predict pixels from the target star,
  provided they are at large-enough time lags that they don't overlap (in time)
  the signals of interest.
That is, if the model is designed to fit not just spacecraft variability
  but also intrinsic stellar variability,
  the predictive model will be permitted to use as input pixels that \emph{do} overlap the target star.
In what follows, we are only going to use input data that do not overlap that target star pixels.
These models ought to remove spacecraft variability but not intrinsic stellar variability.

@@

In addition, each training data set within which we set the parameters (by optimization) has a finite total time extent $t_{\max}\approx 90$\,d.
The train-and-test framework, which includes data out to time $t_{\max}$ but excludes data within $\Delta t$ of the test data,
  effectively assumes that the signals worth preserving have time-scales less than $\Delta t$ but don't recur on time-scales
  shorter than $t_{\max}$.
Those assumptions are good for our purposes but not necessarily ideal for all users:
Short-period exoplanets and certain kinds of stellar variability
  could be wiped out by a model with these settings of the training-data regime.

@@

In the context of this project, the quantities of interest are the light-curves
  (photometry as a function of time or apparent flux as a function of time)
  for every star.
What we get, for every star, from the data-driven model, is a train-and-test prediction
  for the brightness of every pixel in the patch of the detector relevant to the star,
  along with the residual, or the difference between the measured read-out pixel value and the prediction (data minus prediction).
What will be called the ``\name\ photometry'' in what follows is constructed from what will be called the ``\name\ pixels''.
The \name\ photometry is constructed from the \name\ pixels
  just as the \Kepler\ official SAP photometry is constructed from the \Kepler\ Target Pixel Files;
  that is, by summing pre-defined sets of pixels (with unit weights; see above and below for criticism of this).
The \name\ pixels are constructed from the data-driven model predictions by taking,
  for each pixel in each contiguous data segment (see below),
  the \emph{mean} predicted pixel value (mean over time),
  and adding to it the residuals (data minus prediction) away from the data-driven model prediction.
These \name\ pixels are ``calibrated'' pixels,
  in that the data-driven model has been used to fit out all the variability it can,
  subject to the restrictions imposed by its finite freedom and the train-and-test specification.
The signal---in which exoplanet transits will be found---is fundamentally the observed residual away from this prediction,
  but it has to be added back into the mean prediction to have the right ``baseline'' or zero level.
In short, \name\ will produce prediction pixels, residual pixels, \name\ pixels (mean prediction plus residual),
  and aperture-based \name\ photometry analogous to the SAP photometry.

Finally, the fifth general idea is that there is no objective \emph{ground truth} against which we can tell
  that any particular data-driven model is better or worse than any other.
This problem is a problem for \name, and for the \Kepler\ PDC, and any other data-driven calibration models.
One might think that the ``best'' model is the one that predicts data with lowest variance;
  this would be true if all models adhered to the same train-and-test framework, which they don't.
Besides, a model that can predict not just the spacecraft-induced variability,
  but also variability caused by exoplanet transits of interest,
  will effectively over-fit and distort the most important information in the light-curves.
That is, what is considered best for modeling the data depends on the objectives of the user.
For us, who are interested (in the long term) in finding and characterizing Earth analogs,
  the ``best'' data-driven model is the one that produces the most success in finding and characterizing Earth analogs!
What we will show in what follows is that the \name\ photometry does not distort
  artificial exoplanet transit signals injected into real \Kepler\ pixel-level data.
We can also show that it produces stellar light-curves that look sensible for known variable stars.
We cannot yet show that it is optimal for our long-term goals,
  nor can we show that it produces pixelss or light-curves that are more accurately calibrated;
  we will only show promising properties of the \name\ outputs.
In the end, the value of the \name\ will be demonstrated by the scientific projects it enables.

\section{\name\ specification and hyper-parameters}

Each individual \Kepler\ target star is, for each quarter (each 90-ish-day period),
  on a particular CCD on the \Kepler\ focal plane.
Associated with each target star is some set of pixels,
  located in a small contiguous patch more-or-less centered on the target star,
  and telemetered down once for every 30-min exposure.
(Here we are ignoring all short-cadence data that is taken in a different mode with shorter exposures.)
That is, each telemetered pixel in each CCD is associated with a particular \Kepler\ target star.

Let's consider a particular pixel $m$ in the focal plane in one particular quarter.
In that quarter, the spacecraft delivers $N\sim 4000$ measurements $I_{mn}$
  of the intensity falling in that pixel at the $N$ times $t_n$ at which exposures were taken during the quarter.
(For intensity measurements $I_{mn}$ here we are using pixels from the Target Pixel Files.)
We want to build a prediction for the intensity $I_{mn}$ in pixel $m$ at each time $t_n$
  using the intensities $I_{m'n}$ of other pixels $m'$.
The question is:  What other pixels to choose?
There are many possible qualitatively and quantitatively different choices here.
Somewhat arbitrarily,
  we choose all the pixels $m'$ associated with the $Q=5$ stars on the same CCD in the same quarter
  that are closest in magnitude
  (\Kepler\ magnitude as reported in the \Kepler\ Input Catalog)
  to the target star associated with pixel $m$.
This set of pixels%
  ---from the $Q$ stars on the same CCD---%
  is the \emph{pixel set} $\set{M}_m$ associated with pixel $m$.
Note that because the set $\set{M}_m$ is of pixels associated with \emph{different} stars
  than the star associated with pixel $m$,
  the pixel $m$ will not be in the set $\set{M}_m$,
  and nor will any of pixel $m$'s close neighbors.
That is, there will be no (or almost no) overlap in stellar illumination of pixel $m$
  and the pixels $m'\in\set{M}_m$.

When we are predicting the measurement $I_{mn}$ from pixel $m$ at a particular time $t_n$,
  we are going to use a train-and-test framework in which not only do we not use
  data at time $t_n$ in optimizing the parameters of the regression or fit,
  but we don't even use any times $t$ such that $|t-t_n| < \Delta t$,
  where $\Delta t\sim 12$\,h.
That is, we train (optimize fit parameters) using the \emph{time set} $\set{N}_n$ of time
  indices $n'$ such that for all $n'\in\set{N}_n$,
  $t_{n'}$ is in the same quarter as $t_n$,
  and $|t_{n'} - t_n|>\Delta t$.
The time set of indices $\set{N}_n$ therefore does not overlap the time point $t_n$,
  nor any of its neighbors in a time window of half-width $\Delta_t$.

\todo{DFM: Do we want a schematic figure or cartoon which illustrates all of this?}

In addition to the other data (from pixels $m'\in\set{M}_m$ and taken at time points $n'\in\set{N}_n$)
  used to make each prediction, we will use also some \emph{meta-data};
  these include the time itself $t_n$,
  the sine and cosine of the parallactic angle $\theta(t_n)$,
  and the dot product $\hat{n}\cdot v(t_n)$ of the spacecraft velocity $v(t_n)$
  with the direction $\hat{n}$ towards the \Kepler\ field center.
These additional meta-data variables permit the data-driven model
  to capture easily variations induced in the data
  by proper motions, parallaxes, and stellar aberration.
Symbolically, we will denote these $K=4$ pieces of meta-data $d_{kn}$.

As mentioned above, in the context of this project,
  a model is something that can predict data given settings of some parameters,
  and an objective function that can be used to find best values for those parameters.
We prefer to work in a probabilistic mode in which the objective function can be justified
  in terms of a likelihood (probability for the data given the model)
  or a posterior probability density function (likelihood times a prior pdf).
The \name\ treats each \Kepler\ data point $I_{mn}$ as being
  predictable from a linear combination of data points $I_{m'n}$,
  where $m'$ is from the set of non-overlapping pixels $m'\in\set{M}_m$.
\begin{eqnarray}
I_{mn}         &=& I^{\ast}_{mn} + e_{mn}
\\
I^{\ast}_{mn}  &=& \sum_{m'\in\set{M}_m} a_{mnm'}\,I_{m'n} + \sum_{k=1}^{K} b_{mnk}\,d_{kn}
\quad,
\end{eqnarray}
where $I^{\ast}_{mn}$ is the prediction (by the model) for data point $I_{mn}$,
  $e_{mn}$ is a noise contribution or residual away from the prediction,
  and the $a_{mnm'}$ and $b_{mnk}$ are the parameters (linear coefficients of the prediction).
The parameters $a_{mnm'}$ and $b_{mnk}$ have indices $m$ because
  they are different for every pixel $m$,
  and they will even be different for every time step $n$;
  that is, there will be a separate best-fit value for the parameters for every $I_{mn}$.
If we presume that the residuals away from the prediction are normally distributed with zero mean
  and known variance,
  likelihood optimization reduces to chi-squared minimization.
We add to the standard chi-squared definition a regularization term
  (equivalent to multiplying the likelihood by a Gaussian prior pdf)
  that penalizes large absolute values for the the coefficients $a_{mnm'}$:
\begin{eqnarray}
\chi^2_{mn}    &=& \sum_{n'\in\set{N}_n} \frac{[I_{mn'} - I^{\ast}_{mnn'}]^2}{\sigma^2_{mn'}}
                 + \sum_{m'\in\set{M}_m} \frac{a_{mnm'}^2}{\Sigma^2}
\\
I^{\ast}_{mnn'} &=& \sum_{m'\in\set{M}_m} a_{mnm'}\,I_{m'n'} + \sum_{k=1}^{K} b_{mnk}\,d_{kn'}
\quad,
\end{eqnarray}
where the $\sigma^2_{mn'}$ are the (presumed known) individual-pixel noise variances,
  and $\Sigma^2$ sets the strength of the regularization (or width of the prior pdf).
Although the variances $\sigma^2_{mn'}$ are in principle different for every time step $n'$,
  for nearly-constant stars in good data, there is not much variation;
  in what follows, we treat these uncertainties as fixed at
  \todo{DFM: some mean value (we can't ignore this,
   because it ``plays off against'' the regularization)}
The regularization variance $\Sigma^2$ we set to 0.3 (\todo{DFM TAKE NOTE; that's about 10 for the parameter you usually use.})
  because we expect almost all the coefficients $a_{mnm'}$ to be less than unity in magnitude.
We do not regularize the meta-data coefficients $b_{mnk}$,
  because we want the model to make use of the (easily interpretable) meta-data coefficients as much as possible.

The train-and-test idea comes into the objective function $\chi^2_{mn}$:
When we are computing the objective function $\chi^2_{mn}$,
  we are using only time points $n'\in\set{N}_n$ that don't overlap the target (or test) time point $n$.
We train the model---that is, set the parameters $a_{mnm'}$ and $b_{mnk}$---%
  by choosing the full set of parameters that jointly minimize the objective function $\chi^2_{mn}$.
Fortunately, given the form of the model,
  this minimization is just a linear solve (linear operation on the data).
Importantly however, and perhaps surprisingly, the objective function $\chi^2_{mn}$ is \emph{different}
  for every target data point (pixel value to be predicted) $I_{mn}$;
  we have to do an \emph{independent optimization} (or really linear solve)
  of the parameters for every pixel value we want to predict.
That is, every pixel datum $I_{mn}$ we predict will have
  \emph{different} settings of the parameters $a_{mnm'}$ and $b_{mnk}$.
Since there are of order $10^{6}$ total pixel values in the \Kepler\ Target Pixel Files for \emph{each \Kepler\ target},
  and of order $10^7$ data sources used as basis functions in the linear fitting,
  this represents one fuck of a lot of linear solves,
  and a lot of parameters to obtain and record.

For this reason---\emph{so many solves}---%
  we do \todo{some crazy clever stuff} to make this work fast;
  \todo{DFM implementation notes here}.

>>>>

\usepackage{graphicx}
\usepackage{caption} 
\usepackage{subcaption}

\usepackage{hyperref}
\usepackage{url}

\graphicspath{{figures/}}

@@

\title{
  Calibrating the pixel-level Kepler imaging data with a causal data-driven model
 \\ 
}
\author{%
  Dun~Wang\altaffilmark{\ref{CCPP}},
  Dan~Foreman-Mackey\altaffilmark{\ref{CCPP}},
  David~W.~Hogg\altaffilmark{\ref{CCPP},\ref{CDS},\ref{MPIA},\ref{email}},
  Bernhard~Sch\"olkopf\altaffilmark{\ref{MPIIS}},
  others%
}
\newcounter{address}
\setcounter{address}{1}
\altaffiltext{\theaddress}{\stepcounter{address}\label{CCPP}%
  Center for Cosmology and Particle Physics, Department of Physics, New York University}
\altaffiltext{\theaddress}{\stepcounter{address}\label{CDS}%
  Center for Data Science, New York University}
\altaffiltext{\theaddress}{\stepcounter{address}\label{MPIA}%
  Max-Planck-Institut f\"ur Astronomie, Heidelberg, Germany}
\altaffiltext{\theaddress}{\stepcounter{address}\label{email}%
  To whom correspondence should be addressed; \texttt{<david.hogg@nyu.edu>}.}
\altaffiltext{\theaddress}{\stepcounter{address}\label{MPIIS}%
  Max-Planck-Institut f\"ur Intelligente Systeme, T\"ubingen}

\begin{abstract}
In general, astronomical observations are affected by several kinds of noise, each with it's own causal source; there is photon noise, stochastic source variability, and residuals coming from imperfect calibration of the detector or telescope. In particular, the precision of NASA Kepler photometry for exoplanet science—the most precise photometric measurements of stars ever made—appears to be limited by unknown or untracked variations in spacecraft pointing and temperature, and unmodeled stellar variability. Here we present the Causal Pixel Model (CPM) for Kepler data, a data-driven model intended to capture variability but preserve transit signals. The CPM works at the pixel level (not the photometric measurement level); it can capture more fine-grained information about the variation of the spacecraft than is available in the pixel-summed aperture photometry. The basic idea is that CPM predicts each target pixel value from a large number of pixels of other stars sharing the instrument variabilities while not containing any information on possible transits at the target star. In addition, we use the target star’s future and past (auto-regression). By appropriately separating the data into training and test sets, we ensure that information about any transit will be perfectly isolated from the fitting of the model. The method has four hyper-parameters (the number of predictor stars, the auto-regressive window size, and two L2-regularization amplitudes for model components), which we set by cross-validation. We determine a generic set of hyper-parameters that works well on most of the stars and apply the method to a corresponding set of target stars. For these stars, we calculate the Combined Differential Photometric Precision (CDPP), which indicate the noise level of a certain time scale. We find that we can consistently outperform (for the purposes of exoplanet detection) the Kepler Pre-search Data Conditioning (PDC) method for exoplanet discovery.

\end{abstract}

@@

One such method---one that is designed to describe or model spacecraft-induced problems
  but \emph{not} interfere with measurements of stellar variability---%
  is the \Kepler\ Presearch (\sic) Data Conditioning (PDC) method (\todo{citation}).
The PDC ``de-trends'' the \Kepler\ lightcurves by fitting them with a small set of basis lightcurves
  generated from a principal components analysis (PCA) of filtered lightcurves.
That is, it uses data to predict data,
  regularizing the fit (and avoiding over-fitting) by filtering and restricting the dimensionality (through PCA).
The method proposed here, \name, is very similar in spirit to the PDC.
The main differences are
  (1)~that \name\ works in the pixel domain, not the lightcurve domain, so it has access to more fine-grained information,
  (2)~that \name\ has far more freedom (far more parameters) than the PDC
  but it strictly avoids over-fitting the lightcurves on exoplanet-transit time-scales
  through strong regularization and a train-and-test framework, and
  (3)~that purpose of the \name\ is to search for exoplanets, so in \name, intrinsic stellar
  variability is also removed as well as the systematics.
The two methods (\name\ and PDC) are similar however,
  in that they both make the assumption that whatever spacecraft effects are imprinting variability on a stellar lightcurve
  must also be imprinting similar or related variability on other lightcurves.
They also assume that the relationships can be captured with linear models.
By going to the pixel level (unlike the PDC, which works at the photometry level),
  \name\ makes it easier for the model to capture variability
  that is coming through variations in the centroids and point-spread function
  from spacecraft pointing, roll, and temperature.

@@

\section{Causal data-driven model}

@@

The second general idea about data-driven modeling is the investigator's beliefs
  about the causal processes that generate the data
  are crucial in restricting the kinds of data that can be used as input to the model.
That is, different assumptions about the physical properties of the data
  and the data-taking system
  lead to different structures for the data-driven model.
In the case of \Kepler\ data, if we examine two arbitrary stars far away from each other 
on the same CCD as in Fig~\ref{ccd} (every grid in the plot is a pixel light curve time 
series), we can obviously see that the two stars that are hundreds pixel away from each 
other do have similar trends. If we believe that different stars in the \Kepler\ field vary 
independently (that is, are not physically synchronized in any way) because of the 
distance between them, then the only reason that one star might show variability that is strongly \emph{predictive} (useful for prediction) of another star's variability
  is that both stars are being observed by the same device or spacecraft.
That is, one star's pixels can be used to predict another star's pixels
  inasmuch as spacecraft issues imprint on both stars in related ways;
  they share a common cause---the systematics.  
For another example, if we think the spacecraft is being affected by
  processes that take place over time-scales longer than a single read-out
  (for example, thermal processes),
  then it would be sensible to model the data at time $t$ using not just simultaneous data, but also data from a range of times around $t$.
For another example, if an investigator doesn't care about preserving stellar variability,
  and just wants to detect exoplanet transits (say),
  pixels from the target star can be used to predict pixels from the target star,
  provided they are at large-enough time lags that they don't overlap (in time)
  the signals of interest.
That is, if the model is designed to fit not just spacecraft variability
  but also intrinsic stellar variability,
  the predictive model will be permitted to use as input pixels that \emph{do} overlap the 
  target star.
In what follows, we are going to use input data both from pixels of other stars and the  
target star pixels' past and furture.
These models ought to remove both spacecraft variability and intrinsic stellar variability, 
which is optimal for exoplanet transit searching.

\begin{figure}[htb]
\centering
\begin{subfigure}[htb]{0.48\columnwidth}
\includegraphics[width=\columnwidth]{5088536-5}
\caption{}
\end{subfigure}%
\hfill
\begin{subfigure}[htb]{0.48\columnwidth}
\includegraphics[width=\columnwidth]{5949551-5}
\caption{}
\end{subfigure}
\caption{\label{ccd} Stars on the same CCD share systematic errors. The two panels show pixel fluxes (brightnesses) for two stars: (a) KIC 5088536, (b) KIC 5949551; here, KIC stands for Kepler Input Catalog. Both stars lie on the same CCD (see Fig.~\ref{fig1}), but far enough apart such that there is no stray light from one affecting the other. Each panel shows the pixels contributing to the respective star. Note that there exist similar trends in these two stars, caused by systematic errors. 
%The idea of our approach is to predict each pixel from a set of pixels from other stars in order to remove those systematics.
}
\end{figure}

@@

In addition, each training data set within which we set the parameters (by optimization) has a finite total time extent $t_{\max}\approx 30$\,d.
The train-and-test framework, which includes data out to time $t_{\max}$ but excludes data within $\Delta t$ of the test data,
  effectively assumes that the signals worth preserving have time-scales less than $\Delta t$ but don't recur on time-scales
  shorter than $t_{\max}$.
Those assumptions are good for our purposes but not necessarily ideal for all users:
Short-period exoplanets and certain kinds of stellar variability
  could be wiped out by a model with these settings of the training-data regime.

@@

Finally, the fifth general idea is that there is no objective \emph{ground truth} against which we can tell
  that any particular data-driven model is better or worse than any other.
This problem is a problem for \name, and for the \Kepler\ PDC, and any other data-driven calibration models.
One might think that the ``best'' model is the one that predicts data with lowest variance;
  this would be true if all models adhered to the same train-and-test framework, which they don't.
Besides, a model that can predict not just the spacecraft-induced variability,
  but also variability caused by exoplanet transits of interest,
  will effectively over-fit and distort the most important information in the light-curves.
That is, what is considered best for modeling the data depends on the objectives of the user.
For us, who are interested (in the long term) in finding and characterizing Earth analogs,
  the ``best'' data-driven model is the one that produces the most success in finding and characterizing Earth analogs!
What we will show in what follows is that the \name\ photometry does not distort
  artificial exoplanet transit signals injected into real \Kepler\ pixel-level data.
  and promising properties of the \name\ outputs.
In the end, the value of the \name\ will be demonstrated by the scientific projects it enables.

\section{\name\ specification and hyper-parameters}
\subsection{\name\ model}
Each individual \Kepler\ target star is, for each month (here we always use data per month rather than quarter,  
since there is discontinuity between every 30-ish-day period),
  on a particular CCD on the \Kepler\ focal plane.
Associated with each target star is some set of pixels,
  located in a small contiguous patch more-or-less centered on the target star,
  and telemetered down once for every 30-min exposure.
(Here we are ignoring all short-cadence data that is taken in a different mode with shorter exposures.)
That is, each telemetered pixel in each CCD is associated with a particular \Kepler\ target star.

Let's consider a particular pixel $m$ in the focal plane in one particular month.
In that quarter, the spacecraft delivers $N\sim 1300$ measurements $I_{mn}$
  of the intensity falling in that pixel at the $N$ times $t_n$ at which exposures were taken during the month.
(For intensity measurements $I_{mn}$ here we are using pixels from the Target Pixel Files.)
We want to build a prediction for the intensity $I_{mn}$ in pixel $m$ at each time $t_n$
  using the intensities $I_{m'n}$ of other pixels $m'$.
The question is:  What other pixels to choose?
There are many possible qualitatively and quantitatively different choices here.
Somewhat arbitrarily,
  we choose all the pixels $m'$ associated with the $Q$ stars on the same CCD in the same quarter
  that are closest in magnitude
  (\Kepler\ magnitude as reported in the \Kepler\ Input Catalog)
  to the target star associated with pixel $m$.
This set of pixels%
  ---from the $Q$ stars on the same CCD---%
  is the \emph{pixel set} $\set{M}_m$ associated with pixel $m$.
   To rule out any direct optical cross-talk by stray
light, we require that the predictor pixels are from stars
sufficiently far away from the target star (at least 20 pixels
distance on the CCD).
Note that because the set $\set{M}_m$ is of pixels associated with \emph{different} stars
  than the star associated with pixel $m$, and are far from it on CCD, 
  the pixel $m$ will not be in the set $\set{M}_m$,
  and nor will any of pixel $m$'s close neighbors.
That is, there will be no (or almost no) overlap in stellar illumination of pixel $m$
  and the pixels $m'\in\set{M}_m$.

When we are predicting the measurement $I_{mn}$ from pixel $m$ at a particular time $t_n$,
  we are going to use a train-and-test framework in which not only do we not use
  data at time $t_n$ in optimizing the parameters of the regression or fit,
  but we don't even use any times $t$ such that $|t-t_n| < \Delta t$,
  where $\Delta t\sim 10$\,h as shown in Fig.~\ref{train-and-test}.
That is, we train (optimize fit parameters) using the \emph{time set} $\set{N}_n$ of time
  indices $n'$ such that for all $n'\in\set{N}_n$,
  $t_{n'}$ is in the same quarter as $t_n$,
  and $|t_{n'} - t_n|>\Delta t$.
The time set of indices $\set{N}_n$ therefore does not overlap the time point $t_n$,
  nor any of its neighbors in a time window of half-width $\Delta_t$.

\begin{figure}[htb]
\centering
\includegraphics[width=0.8\columnwidth]{train_and_test}
\caption{\label{train-and-test} Train-and-test framework. Data near the target point $t_{n}$ within $\Delta t$ is excluded in the training set}
\end{figure}

In addition to pixel set $m'\in\set{M}_m$ from other stars,  we also include
past and future of the target star --- autoregressive (AR) component as input to remove 
more of the stellar variability and thus increase the sensitivity for transits. To do this, 
we select an exclusion window of half-width $\Delta t$ including R data points, 
where $\Delta t\sim 10$ (as big 
as the window in train-and-test framework) around the point of time $t_{n}$ being 
corrected, to ensure that we do not remove the transit itself and then use S closest 
future and past time points. That is, for every pixel m in the target star , we construct S virtual time series, in which every component v is defined to be     
\begin{eqnarray}
I_{vn} = I_{mn-R-k}\ or\ I_{vn} = I_{mn+R+k},
\quad,
\end{eqnarray}
where k = 0, 1, ..., S, so if there are totally M pixels in the target stars, we will finally add 
$2\cdot M\cdot S$ autoregressive components into the predictors,  which construct the autoregressive set $\set{V}_m$

As mentioned above, in the context of this project,
  a model is something that can predict data given settings of some parameters,
  and an objective function that can be used to find best values for those parameters.
We prefer to work in a probabilistic mode in which the objective function can be justified
  in terms of a likelihood (probability for the data given the model)
  or a posterior probability density function (likelihood times a prior pdf).
The \name\ treats each \Kepler\ data point $I_{mn}$ as being
  predictable from a linear combination of data points $I_{m'n}$,
  where $m'$ is from the set of non-overlapping pixels $m'\in\set{M}_m$.
\begin{eqnarray}
I_{mn}         &=& I^{\ast}_{mn} + e_{mn}
\\
I^{\ast}_{mn}  &=& \sum_{m'\in\set{M}_m} a_{mnm'}\,I_{m'n} + \sum_{v\in\set{V}_m} b_{mnv}\,I_{vn}
\quad,
\end{eqnarray}
where $I^{\ast}_{mn}$ is the prediction (by the model) for data point $I_{mn}$,
  $e_{mn}$ is a noise contribution or residual away from the prediction,
  and the $a_{mnm'}$ and $b_{mnk}$ are the parameters (linear coefficients of the prediction).
The parameters $a_{mnm'}$ and $b_{mnk}$ have indices $m$ because
  they are different for every pixel $m$,
  and they will even be different for every time step $n$;
  that is, there will be a separate best-fit value for the parameters for every $I_{mn}$.
If we presume that the residuals away from the prediction are normally distributed with zero mean
  and known variance,
  likelihood optimization reduces to chi-squared minimization.
We add to the standard chi-squared definition a regularization term
  (equivalent to multiplying the likelihood by a Gaussian prior pdf)
  that penalizes large absolute values for the the coefficients $a_{mnm'}$:
\begin{eqnarray}
\chi^2_{mn}    &=& \sum_{n'\in\set{N}_n} \frac{[I_{mn'} - I^{\ast}_{mnn'}]^2}{\sigma^2_{mn'}}
                 + \lambda_{a}\sum_{m'\in\set{M}_m}a_{mnm'}^2 + \lambda_{b}\sum_{v\in\set{V}_m}b_{mnv}^2
\\
I^{\ast}_{mnn'} &=& \sum_{m'\in\set{M}_m} a_{mnm'}\,I_{m'n'} + \sum_{v\in\set{V}_m} b_{mnv}\,I_{vn'}
\quad,
\end{eqnarray}
where the $\sigma^2_{mn'}$ are the (presumed known) individual-pixel noise variances,
  and $\lambda_{a}$, $\lambda_{b}$ set the strength of the regularization (or width of the prior pdf) for parameters $a_{mnm'}, b_{mnv}$.

The train-and-test idea comes into the objective function $\chi^2_{mn}$:
When we are computing the objective function $\chi^2_{mn}$,
  we are using only time points $n'\in\set{N}_n$ that don't overlap the target (or test) time point $n$.
We train the model---that is, set the parameters $a_{mnm'}$ and $b_{mnv}$---%
  by choosing the full set of parameters that jointly minimize the objective function $\chi^2_{mn}$.
Fortunately, given the form of the model,
  this minimization is just a linear solve (linear operation on the data).
Importantly however, and perhaps surprisingly, the objective function $\chi^2_{mn}$ is \emph{different}
  for every target data point (pixel value to be predicted) $I_{mn}$;
  we have to do an \emph{independent optimization} (or really linear solve)
  of the parameters for every pixel value we want to predict.
That is, every pixel datum $I_{mn}$ we predict will have
  \emph{different} settings of the parameters $a_{mnm'}$ and $b_{mnk}$.
Since there are of order $10^{6}$ total pixel values in the \Kepler\ Target Pixel Files for \emph{each \Kepler\ target},
  and of order $10^7$ data sources used as basis functions in the linear fitting,
  this represents one fuck of a lot of linear solves,
  and a lot of parameters to obtain and record.

Once we have obtained the parameters $a_{mnm'}$ and $b_{mnv}$ corresponding to a particular data point $I_{mn}$,
  we can make a \emph{prediction} $I^{\ast}_{mn}$ for the intensity at that pixel.
By construction of our objective function, this is truly a prediction,
  in the sense that the optimization (or solve) that produced the parameters
  (and thus the prediction)
  did not make use of $I_{mn}$ itself,
  or even any of the pixel values that are nearby in angle or time
  (as described above).
  With all the predicted pixel values $I^{\ast}_{mn}$ of the target star,  
  our new stellar flux estimates,
  what we will call the ``\name\ prediction'',
  is constructed from the \name\ pixels
  in precisely the same way as the official \Kepler\ SAP photometry
  is constructed from the Target Pixel Files.
That is, we perform a weighted sum of \name\ predicted pixels $I^{\ast}_{mn}$ with weights $w_m$,
  all of which are either zero or unity,
  and we adopt precisely the same weight assignments as are adopted in the SAP photometry;
  in equations, the flux estimate $S_n$ at time $t_n$ of the target star is given by
\begin{eqnarray}
S_n = \sum_m w_m\,I^{\ast}_{mn}
\quad ,
\end{eqnarray}
where the sum is over the $M$ pixels that are associated with the target star.
As we have noted above and below, these photometric estimators are not optimal for any purpose,
  but improving them is beyond the scope of this project.
